\documentclass[oneside,a4paper]{book}

\usepackage{float}

\input{preamble}
\chapter*{\centering Abstract}
\begin{quotation}
\noindent 

Sound source localization is a well-known problem in the field of signal processing. It is used in many domains, such as robotics, surveillance, and military applications. This project aims to create a baseline to develop a system to localize a sound source in an open environment. We base our project on a neural network that takes a spectrogram as input and predicts the position of a vehicle. We train the neural network using a dataset of sounds recorded from vehicles on the street. We also use a simulation to augment the dataset. To make the model safe, we test it against adversarial attacks to understand how it behaves if someone attacks is.

\vspace{215pt}

{ centering
Supervisors:
\vspace{7.5pt}

Michael Mäder: Professor in computer science

Beat Wolf: Professor in computer science
\vspace{7.5pt}

Principals
\vspace{7.5pt}

Marc-Antoine Fénart: Professor in civil engineering

Gabriel Python: Scientific associate at Rosas

}
\end{quotation}
\clearpage
\chapter*{\centering Acknowledgements}

I want to express my gratitude to my supervisors, Michael Mäder and Beat Wolf, for the opportunity to realize this Master's thesis with their supervision and for their excellent advice during this project. I also want to thank Marc-Antoine Fénart for the help with the baseline definition and the lent material. Additionally, I want to thank Gabriel Python and every member of the Rosas team for their help, advice, and encouragement during this project. 
Finally, I would like to thank my family and friends for the support they provided during the realization of this project.

\newpage

% Acronym table

\chapter*{\centering Acronyms}
\begin{acronym}[TDMA]
    \acro{HEIA-FR}{Haute École d'Ingénierie et d'Architecture de Fribourg} 
    \acro{HES-SO}{Haute École Spécialisée de Suisse Occidentale (University of Applied Sciences and Arts Western Switzerland)}
    \acro{AI}{Artificial Intelligence}
    \acro{DNN}{Deep Neural Network}
    \acro{CNN}{Convolutional Neural Network}
    \acro{GPU}{Graphics Processing Unit}
    \acro{CPU}{Central Processing Unit}
    \acro{RAM}{Random Access Memory}
    \acro{MPEG}{Moving Picture Experts Group}
    \acro{ffmpeg}{Fast Forward MPEG}
    \acro{SSH}{Secure Shell Protocol}
    \acro{RTP}{Real-time Transport Protocol}
    \acro{SFTP}{Secure File Transfer Protocol}
    \acro{FFT}{Fast Fourier Transform}
    \acro{PCM}{Pulse-code Modulation}
    \acro{FGSM}{Fast Gradient Sign Method}
    \acro{WAV}{Waveform Audio File Format}
    \acro{MP4}{MPEG-4}
\end{acronym}




\tableofcontents



\include{Chapters/1_Introduction}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{Chapters/2_Background}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{Chapters/3_Methodology}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{Chapters/4_Setup}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{Chapters/5_Results}
\newpage{\pagestyle{empty} \cleardoublepage}


\include{Chapters/6_Conclusions}
\newpage{\pagestyle{empty} \cleardoublepage}


\begin{appendix}
\include{Chapters/appendix}
\newpage{\pagestyle{empty} \cleardoublepage}
\end{appendix}

\addcontentsline{toc}{chapter}{\numberline{}List of Tables}
\listoftables

\addcontentsline{toc}{chapter}{\numberline{}List of Figures}
\listoffigures

\addcontentsline{toc}{chapter}{\numberline{}Bibliography}

\bibliography{Bibliography/libs}
\bibliographystyle{unsrt}

%END Doc
%-------------------------------------------------------

\end{document}

